\text{Additive drift with tail bounds}

### 2021-09-08 article.tex
add bounds for sum of lambdas and fix bounds

\section{Tail bounds}
\cm
\section{Time bounds for process with variable $\lambda$}
\cm

>>>>

\section{Tail bounds}
\subsection{Upper bounds}
\cm
\subsection{Lower bounds}
Lets take a look on process $\{X_t\}$ and its derive derivative process $\{Y_t\}$, where $Y_t = \varepsilon t - X_t$ and it has negative drift.

Then we want to bounds $\Pr[T_x > t_0]$, where $T_x$ - first time $X_t \geq b$.

\begin{align*}
    \Pr[T_x > t_0] \leq \Pr[X_{t_0} < b] \leq \Pr[Y_{t_0} > \varepsilon t_0 - b]
\end{align*}

Then, because $\{Y_t\}$ - process with negative drift, we may use the corresponding theorem *label*:

\begin{align*}
    \Pr[Y_t > \varepsilon t_0 - b] \leq t_0 D p e^{-\gamma(\epsilon t_0 - b + a)}
\end{align*}

Lets rewrite some to $T_x$:

\begin{align*}
    \Pr[T_x > t_0] \leq t_0 D p e^{-\gamma(\epsilon t_0 - b + a)}
\end{align*}

Replace $t_0$ with another expression:

\begin{align*}
    t_0 := \frac{\alpha (b - a)}{\varepsilon}
\end{align*}

And then:

\begin{align*}
    \Pr\left[T_x > \frac{\alpha (b - a)}{\varepsilon}\right] \leq \frac{\alpha (b - a)}{\varepsilon} D p e^{-\gamma(\alpha - 1)(b - a)}
\end{align*}

\section{Time bounds for process with variable $\lambda$}
\cm
\subsection{Case when $\lambda$ is random value}
Lets calculate total progress $\triangle X$. It is summation of all progresses of each iterations $\triangle X_i$. Then we can define variable $T$ - number of iterations (or time) and also:
\[
    \triangle X = \sum_{i = 0}^{T} \triangle X_i
\]

Then drift of $\triangle X$ is drift of this Vald's equality:

\[
    E[\triangle X] = E\left[\sum_{i = 1}^{T} \triangle X_i\right]      
\]

Lets denote that $E[\triangle X_i]$ is a constant or we can show lower and upper bounds. Then:
\[
    E[\triangle X] = E\left[\sum_{i = 1}^{T} \triangle X_i\right] \thickapprox E[T] E[\triangle X_i]      
\]

Our goal to estimate total progress ($\Lambda$) by total cost, which is total number of calculations (number of calculations on iteration $i$ equals $\lambda_i$). Because $\lambda$ is random variable, each $\lambda_i$ has same drift and then:
\[
    E\left[\Lambda\right] = E\left[\sum_{i = 1}^{T} \lambda_i\right] = E[T] E[\lambda]    
\]

And then: 
\[
        E[\Lambda] = \frac{E[\triangle X] E[\lambda]}{E[\triangle X_i]}
\]

Lets denote $\vartheta_\lambda = \frac{E[X_i]}{E[\lambda]}$ and simplify previous equation:
\[
        E[\Lambda] = \frac{E[\triangle X]}{\vartheta_\lambda}
\]
